---
title: "BCOR and KDM2B Target Gene Analysis in GCB-DLBCL"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
peak_totals <- read.csv("results/tables/peak_totals.csv", stringsAsFactors = FALSE)
region_summary <- read.csv("results/tables/genomic_region_summary.csv", stringsAsFactors = FALSE)
candidate_genes <- read.csv("results/tables/candidate_target_genes.csv", stringsAsFactors = FALSE)
thesis_counts <- read.csv("results/tables/thesis_count_comparison.csv", stringsAsFactors = FALSE)
if (file.exists("results/tables/go_enrichment.csv")) {
  go_terms <- read.csv("results/tables/go_enrichment.csv", stringsAsFactors = FALSE)
  go_source_label <- "Current rerun GO enrichment output"
} else {
  go_terms <- read.csv("results/tables/go_terms_summary.csv", stringsAsFactors = FALSE)
  go_source_label <- "Thesis-reported GO summary placeholder"
}
```

## Overview

This report summarizes the thesis subsection on identification of putative PRC1.1 target genes in GCB-type DLBCL using public ChIP-seq data from the `LY1` cell line.

Peak annotations were generated with `HOMER`, overlap between `BCOR` and `KDM2B` was used to define a shared PRC1.1-associated set, and `H3K27me3` was used to exclude candidate regions likely shared with `PRC2`.

## Peak Summary

```{r peak-table}
knitr::kable(peak_totals, align = c("l", "r"))
```

Key observations from the thesis text:

- `14,546` peaks overlapped between `BCOR` and `KDM2B`.
- `6,943` overlapping peaks were assigned to promoter-TSS or intronic regions.
- `11,925` peaks were unique to `KDM2B`.
- `3,002` peaks were unique to `BCOR`.

## Thesis Count Comparison

```{r count-comparison}
knitr::kable(thesis_counts, align = c("l", "r", "r"))
```

The current public rerun reproduces the reported BCOR, KDM2B, overlap, and Venn-style unique counts when the overlap is defined as distinct BCOR-KDM2B genomic intersection regions.

## Genomic Distribution

```{r region-table}
knitr::kable(region_summary, align = c("l", "l", "r"))
```

The thesis text reports that `6,943` shared peaks were located in promoter-TSS and intronic regions, consistent with promoter-proximal and intragenic binding by PRC1.1-associated factors.

## Biological Process Enrichment

```{r go-table}
knitr::kable(utils::head(go_terms, 20))
```

Source for the table above: `r go_source_label`.

These terms suggest PRC1.1-associated chromatin binding in LY1 cells may regulate protein turnover, cell-cycle control, nucleocytoplasmic trafficking, developmental signaling, and apoptosis-related pathways.

## Candidate Genes

```{r candidate-genes}
knitr::kable(head(candidate_genes, 20), align = c("l", "l"))
```

The current committed candidate gene table is a placeholder seeded with thesis-reported examples. Running the overlap and annotation workflow with the public peak BED files will replace it with a directly generated gene list.

## Figures

Add thesis Figure 31 panels to `results/figures/` and extend this report to embed them:

- `results/figures/figure31a_venn.*`
- `results/figures/figure31b_genomic_regions.*`
- `results/figures/figure31c_go_dotplot.*`

## Reproducibility Notes

- Raw public files are intentionally not committed under `data/raw/`.
- `data/metadata/public_sources.csv` records the GEO accessions used in the thesis.
- `docs/reanalysis_workflow.md` provides the rerun steps for GitHub documentation.
- The committed summary tables currently combine thesis-reported values with rerunnable workflow outputs where raw peak files are available.
